### 2017-05-10 src/3_TimeSeries.tex

\subsection{Spurious regression} \label{sec:spurious}
The use of non-stationary data can lead to spurious regressions. Spurious regression
dates back to Yule in 1926 \cite{yule1926}. If two stationary
variables are generated as independent random series and are trending over time,
when one of those variables is regressed on the other, they could have a high
$R^2$ even if the two are totally unrelated. So, if standard regression
techniques are applied to non-stationary data, it could look good under standard
measures but valueless \cite{brooks2002}.

>>>>

\subsection{Spurious regression} \label{sec:spurious}
The use of non-stationary data can lead to spurious regressions. Spurious
regression dates back to Yule in 1926 \cite{yule1926}. If two stationary
variables are generated as independent random series and are trending over
time, when one of those variables is regressed on the other, they could have a
high $R^2$ even if the two are totally unrelated. So, if standard regression
techniques are applied to non-stationary data, it could look good under
standard measures but valueless \cite{brooks2002}.
The
regression measure $R^2$ gives high values in presence of spurious
relationships. This measure would means that the model explains all the
variability of the response data around its mean which is not true.

The $R^2$ measure is calculated as follows:

\begin{equation}
\label{eq:rsquared}
R^2 = 1 - \frac{\sum_{t=1}^T \epsilon_t^2}{\sum_{t=1}^T(y_t - \bar{y})^2}
\end{equation}

In presence of spurious relationships the denominator of equation
\ref{eq:rsquared} becomes very large because a large weight is placed on
extreme observations on either side of the mean $\bar{y}$.
